Classless Java

### 2015-09-25 paper/sections/Formalization.tex
more formalization

\section{Formal Semantics}\label{sec:typesafety}
\marco{Tentative Grammar ClassLessJava}

@@

Expression Typing:

@@

Context:

@@

Subtyping:

@@

Interface Table (IT):

A mapping from types \texttt{T} to interface declarations \texttt{L}. From the
interface table, we can read off the subtype relation between interfaces. The
subtype relation is given by the \textbf{extends} clauses in \texttt{IT}.

Auxiliary Definitions:

- \textsf{mtype(m, C)} : the signature of method m in C.

@@

\[ \textsf{mmodifier(m, C)} = ? \]

\[ \textsf{mtype(m, C)} = ? \]

\[ \textsf{checksuper(C.super.m(e), A, C)} = ? \]

\yanlin{todo: add auxiliary functions}
\yanlin{todo: add subtyping rules}

\subsection{Auxiliary function: \textsf{mbody}}

@@

\subsection{Auxiliary function: \textsf{shadow}}

@@

\subsection{Auxiliary function: \textsf{replace}}

>>>>

\section{Formal Semantics}\label{sec:formal}
\subsection{Grammar}

\marco{Tentative Grammar ClassLessJava}

@@

\subsection{Typing Rules}
\subsubsection{Expression Typing}

@@

\subsubsection{Context}

@@

\subsubsection{Subtyping}

@@

\subsubsection{Interface Table}
The Interface Table (IT) mapping from types \texttt{T} to interface declarations \texttt{L}. From the
interface table, we can read off the subtype relation between interfaces. The
subtype relation is given by the \textbf{extends} clauses in \texttt{IT}.

\subsection{Auxiliary Definitions}
\yanlin{todo: add more auxiliary functions}

\yanlin{todo: add interface context}

\subsubsection{Auxiliary function: \textsf{mtype}}
- \textsf{mtype(m, C)} : the signature of method m in C.

@@

\subsubsection{Auxiliary function: \textsf{mbody}}

@@

\subsubsection{Auxiliary function: \textsf{shadow}}

@@

\subsubsection{Auxiliary function: \textsf{replace}}
